\resumeSubHeadingListStart
    \resumeProject
      {{\textbf{Runalytix – Intelligent Runbook Validator and Optimizer}} \href{https://youtu.be/aLlhrwAPgxA}{\textit{\small{Video}}} \textbar{} \href{https://docs.google.com/presentation/d/1qt7XzuZkbnZ_yUeG8MJ2ZQZqVL7QH2_8/edit?slide=id.p1\#slide=id.p1}{\textit{\small{Design Doc}}}}
      {}
      {May 2025}
      {}
      \resumeItemListStart
        \item \textbf{Tools \& Technologies:} Python, FastAPI, React, Redux, LangChain, RAG, OpenAI, Nutanix Calm, Epsilon, IDF
        \item Devised \textbf{Runalytix}, an AI assistant for validating and optimizing \textbf{Calm Runbook scripts} in real-time, significantly reducing debugging time by \textbf{~50\%} and enhancing the reliability and performance of C++ cloud infrastructure automation.
        \item Implemented \textbf{LLM-based analysis} to detect syntax, logic, and security issues in Shell, PowerShell, and HTTP tasks, achieving \textbf{~90\% issue detection accuracy} critical for maintaining secure, high-performance, and robust cloud services.
        \item Integrated a context-aware suggestion engine using \textbf{LangChain + RAG}, improving fix recommendation accuracy by \textbf{35\%} and reducing Runbook execution errors by \textbf{~40\%}, contributing to more stable and performant cloud operations and efficient resource management.
      \resumeItemListEnd

    \resumeProject
      {{\textbf{Sustainable Traffic Management system}} \href{https://github.com/shubhamvermaa/Hack_36?tab=readme-ov-file}{\textit{\small{Github}}} \textbar{} \href{https://youtu.be/P73OS4Aaz14}{\textit{\small{Video}}}}
      {}
      {Jan. – Apr. 2024}
      {}
      \resumeItemListStart
        \item \textbf{Tools \& Technologies:} JavaScript, Python, HTML, CSS, Gsheet, SheetDB, P5.js, YoloV4
        \item Used \textbf{Braess's Paradox} to optimize traffic flow, increasing simulated throughput by \textbf{30\%} in dense areas, demonstrating principles of performance optimization for complex distributed systems, relevant to C++ cloud infrastructure.
        \item Developed a \textbf{custom algorithm} to model congestion across \textbf{50+ city layouts}, analyzing flow and bottlenecks, applicable to understanding resource contention and data flow in large-scale distributed cloud infrastructure.
        \item Designed a \textbf{city planning tool} to simulate and evaluate the impact of new road construction in urban layouts, improving traffic efficiency predictions by \textbf{~35\%} and aiding data-driven infrastructure decisions for optimal resource utilization and scalability.
        \item Leveraged \textbf{YOLOv4} for real-time traffic detection from video and trained a routing model to optimize path selection, improving system response speed by \textbf{25\%} and demonstrating low-latency processing and efficient resource allocation.
      \resumeItemListEnd

    \resumeProject
      {{\textbf{Intelligent Chatbot for User Queries}} \href{https://github.com/dubeykirtiman/MNNIT_ChatBot}{\textit{\small{Github}}} \textbar{} \href{https://www.youtube.com/watch?v=mfgmaNysABo}{\textit{\small{Video}}}}
      {}
      {Sep. - Dec. 2023}
      {}
      \resumeItemListStart
        \item \textbf{Tools \& Technologies:} RNN, LSTM, Python, OpenAI (v3.5), NLTK, RASA, Spacy, MySQL, Ngrok, AWS EC2
        \item Built a context-aware chatbot designed for \textbf{MNNIT} and \textbf{Botrush} using intent recognition and dialogue management, achieving \textbf{75\%+ intent classification accuracy} and handling concurrent user interactions as a reliable, scalable service.
        \item Embedded \textbf{OpenAI API (v3.5)} for generating robust fallback responses when user queries fell outside predefined intents, enhancing system resilience and user experience in a distributed service context.
        \item Deployed the bot on \textbf{Telegram}, successfully handling \textbf{100+ user queries} via \textbf{AWS EC2 t2.micro} using \textbf{Ngrok} tunneling, demonstrating experience with cloud deployment, networking fundamentals, and managing services in a Linux environment.
      \resumeItemListEnd
\resumeSubHeadingListEnd